---
title: "LDP Productivity and Reproducibility Project Manuscript"
author: "Madi Philibert"
date: "2025-09-11"
output: pdf_document
bibliography: LDP_PR_2025.bib
link-citations: yes
csl: science.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
```

```{r load-data, include = FALSE}
raw_penguin_data<-read.csv("C:/Users/madip/OneDrive/Desktop/LDP_PR/LDP_Reproducibility_Productivity/00_raw_data/raw_penguin_data.csv")
```

# Introduction

This project, for the Living Data Project's 2025 course on Productivity and Reproducibility, uses the data from the "palmerpenguins" [@horstamhillapgormankbPalmerpenguinsPalmerArchipelago2020] dataset available in R.

## Figures

This is a sample figure made using the "palmerpenguins" data to practice inserting figures into a manusript.

```{r Sample Figure}
ggplot(data = raw_penguin_data, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(
    title = "Bill Length vs Flipper Length in Palmer Penguins",
    x = "BIll Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  ) +
  theme_minimal()
```

Figure 1. Bill length (mm) vs. flipper length (mm) of Palmer penguins.
